Classless Java

### 2015-11-11 paper/sections/RelatedWork.tex
related work on Lombok

\paragraph{Meta-programming techniques}
- MetaFJig*
\yanlin{Maybe Marco can help with the text for MetaFJig?}

@@

>>>>

\paragraph{Meta-programming techniques}
- MetaFJig*~\cite{}
\yanlin{Maybe Marco can help with the text for MetaFJig?}

@@

-Lombok~\cite{} project provides a set of predefined annotations, including
constructor generators similar as ours (\textbf{@NoArgsConstructor},
\textbf{@RequiredArgsConstructor} and \textbf{@AllArgsConstructor}). They
generate various kinds of constructors for \emph{classes}, with or without
constructor arguments. This set of annotations is of great use, especially when
they are used together with other features provided in Lombok (e.g.,
\textbf{@Data}). Moreover, the implementation of these annotations in Lombok
gives us hints on how to implement \mixin. However, none of these annotations
can model what we are doing with \mixin - generating a constructor for
\emph{interfaces}. Apart from constructors, \mixin also provides other
convenient features (including generating fluent setters, type refinement,etc)
that the base Lombok project could not provide.
